% LaTeX resume using res.cls
%\documentclass[11pt]{res}
\documentclass[10pt]{article}
\usepackage{geometry}
\usepackage{pslatex}
\author{Michael Crumrine}
\usepackage{bibentry}
\geometry{tmargin=0.25in,lmargin=0.5in,rmargin=0.5in,bmargin=1in,letterpaper}
\usepackage{url}
\usepackage{enumitem}
\usepackage{natbib}
\DeclareUnicodeCharacter{2009}{ }
\begin{document} 
\nobibliography{pubs.bib}
\bibliographystyle{plainnat}
\nocite{*}
\pagenumbering{gobble}
%\hoffset=20pt
\noindent{\textsc{\Huge{Michael Crumrine}}}

\noindent(414) 213-5928

\noindent crumrine@umn.edu

\section*{\Large{\textsc{Education}}}
\vspace*{-1.5em}
\hrulefill

	\noindent{\bf Ph.D Physics: Experimental Cosmology} \hspace{\fill} {\bf In Progress}
	
	\noindent{\it University of Minnesota} - Minneapolis, MN \hspace{\fill} {\bf Expected Fall 2021}\\
	\noindent School of Physics and Astronomy 
	\vspace{0.125in}
	
	\noindent{\bf B.Sc: Physics and Mathematics} \hspace{\fill} {\bf May 2013}  \\
	\noindent{\it Beloit College} - Beloit, WI
	
	\begin{itemize}[noitemsep,topsep=0pt]
%		\hoffset=20pt\itemsep-0.4em
		\item{Graduated \textit{Magna Cum Laude} with departmental honors in Physics}
	\end{itemize}


\section*{\Large{\textsc{Work Experience}}}
\vspace*{-1.5em}
\hrulefill

	\noindent {\bf Graduate Research Assistant} \hspace{\fill} {\bf 2016 - Present}  \\
	\noindent{\it University of Minnesota} - Minneapolis, MN
	
	\begin{itemize}[noitemsep,topsep=0pt]
		\item{Lead the thermal and mechanical design of a new cryogenic receiver for the Bicep Array experiment including extensive CAD modelling in Solidworks and multiphysics simulation in Comsol.}
		\item{Managed hardware requirements and interfaces between collaborating groups across six institutions. Oversaw manufacturing, integration, testing, and first operations of these new receivers.}
		\item{Deployed to the South Pole for maintenance, re-assembly, and calibration of the Keck and Bicep3 telescopes. Commissioned the new Bicep Array telescope at the geographic South Pole over an intensive 14 week summer season.}
		\item{Responsible for quality analysis of incoming data and investigation of anomalous features to diagnose and solve root-cause problems during operation.}
		\item{Lead analysis of the first year of raw data from the new Bicep Array experiment to produce stricter constraints on polarized galactic synchrotron emission. }
		\item{Prepared and presented technical reports at weekly meetings with 30 + collaborators across six institutions.}
		\item{Mentored incoming graduate students and undergraduate students in experimental procedures and techniques.}		
		\item{Deployed to the South Pole:}
		
			\begin{itemize}[noitemsep,topsep=0pt]
				\item{Nov. 2016 - Jan 2017}
				\item{Nov. 2019 - Feb 2020}
			\end{itemize}
	\end{itemize}
	
	\noindent{\bf Teaching Assistant} \hspace{\fill} {\bf 2014 - 2016}  \\
	\noindent{\it University of Minnesota} - Minneapolis, MN
	
	\begin{itemize}[noitemsep,topsep=0pt]
	\item{Courses: Introduction to Physics for Science and Engineering (2 semesters) and Biology and Pre-Medicine (3 semesters)}
	\end{itemize}
	
	\noindent{\bf SULI Intern} \hspace{\fill} {\bf 2013} \\
	\noindent{\it Lawrence Berkeley National Laboratory} - Berkeley, CA
	
	\begin{itemize}[noitemsep,topsep=0pt]
		\item{Developed a new CBED/STEM imaging mode for the TEAM I
			transmission electron microscope resulting in increased imaging resolution}
	\end{itemize}
	
	\noindent{\bf Fermilab Seasonal Employee} \hspace{\fill} {\bf 2013} \\
	\noindent{\it Fermi National Accelerator Laboratory} - Batavia, IL
	
	\begin{itemize}[noitemsep,topsep=0pt]
		\item{Decommissioned the Collider Detector at Fermilab (CDF)}
	\end{itemize}
	
	\noindent{\bf Scenic Shop Supervisor} \hspace{\fill} {\bf 2010 - 2013} \\
	\noindent{\it Beloit College} - Beloit, WI
	
	\begin{itemize}[noitemsep,topsep=0pt]
		\item{Constructed sets and scenery to specifications for performing arts department}
		\item{Oversaw small groups of student employees, taught proper power tool use, safety, and
			fabrication techniques}
	\end{itemize}

\section*{\Large{\textsc{Skills and Experience}}}
\vspace*{-1.5em}
\hrulefill

\vspace{0.1in}
\noindent Physics, Experiment, Cosmology, Cryogenics, Computer Aided Design (CAD),  Finite Element Analysis (FEA), Solidworks, \mbox{COMSOL},Data Analysis, Matlab, Octave, Mathematica, C++,
	\LaTeX, Python, Scientific Computing\\
\newpage
\section*{\Large{\textsc{Selected Publications}}}
\vspace*{-1.5em}
\hrulefill

\vspace{0.1in} 
	\begin{itemize}[topsep=0pt]
		%\item{\bibentry{bk11}}
		\item{\bibentry{crumrine_2018}}
		\item{\bibentry{bk10}}
		%\item{\bibentry{barkats_2018}}
		\item{\bibentry{jaehwan_2018}}
		\item{\bibentry{Hui_2018}}
		%\item{\bibentry{Soliman_2018}}
	\end{itemize}
\end{document}






























